Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-16 paper.tex
Typo

To help understand---and possibly predict---the $Re$-sensitivity on turbine
performance, a series of static foil coefficient datasets were computed with the
XFOIL viscous panel method code \cite{Drela1989}, a commonly used tool for
airfoil analysis, e.g. \cite{Castelli2011, Walker2014}, implemented as part of
the open source turbine design software QBlade \cite{Marten2013}. Simulations
were run for an angle of attack range of 0--40 degrees, in increments of 0.5
degrees. Solver parameters used a 100 panels, a fixed speed, zero Mach number,
\texttt{NCrit=9} (default $\mathrm{e}^n$ transition criteria parameter for an
average wind tunnel), and no forced boundary layer transition. Characteristics
were computed for the approximate average blade chord Reynolds numbers
encountered in the tow tank experiments.

>>>>

To help understand---and possibly predict---the $Re$-sensitivity on turbine
performance, a series of static foil coefficient datasets were computed with the
XFOIL viscous panel method code \cite{Drela1989}, a commonly used tool for
airfoil analysis, e.g. \cite{Castelli2011, Walker2014}, implemented as part of
the open source turbine design software QBlade \cite{Marten2013}. Simulations
were run for an angle of attack range of 0--40 degrees, in increments of 0.5
degrees. Solver parameters used were 100 panels, a fixed speed, zero Mach
number, \texttt{NCrit=9} (default $\mathrm{e}^n$ transition criteria parameter
for an average wind tunnel), and no forced boundary layer transition.
Characteristics were computed for the approximate average blade chord Reynolds
numbers encountered in the tow tank experiments.
